Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-04-26 paper/main.tex
new numbers

Spot version 2.10.4 and Z3 version 4.8.13 have been used in the
experimental evaluation.

For each automata set (that is, the output of an individual LTL
translator), we have applied all single-level reductions and the
multi-level reduction, always with incremental approach and without
reduction of the number of clauses. The timeout for each QBF query was
set to 30 seconds.
%We have again filtered out the automata for which
%any of the four \telatko runs timed out after 120 seconds. We do this
%to make sure the numbers of acceptance marks can be meaningfully
%compared between different reduction levels of the same automata set.
Additionally, we have filtered one automaton from the \texttt{ltl3tela} set
that cannot be processed by \telatko due to an extensive use of system
resources.

@@

\begin{table}[b]
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
\begin{tabular}{lr@{~~~}lr}
\toprule
tool        & version&homepage & automata \\
\midrule
\texttt{ltl2dela} & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
\texttt{ltl2dgra} & 21.0 & & 234\\
\texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
\texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 90\\
\bottomrule
\end{tabular}
\end{table}

>>>>

Spot version 2.10.4 and Z3 version 4.8.13 have been used in the
experimental evaluation. The experiments have been run on a computer
with Intel® Core™ i7-8550U processor and 16 GB of memory running
Debian 11.

For each automata set (that is, the output of an individual LTL
translator), we have applied all single-level reductions and the
multi-level reduction, always with incremental approach and without
reduction of the number of clauses. The timeout for each QBF query was
set to 30 seconds.
%We have again filtered out the automata for which
%any of the four \telatko runs timed out after 120 seconds. We do this
%to make sure the numbers of acceptance marks can be meaningfully
%compared between different reduction levels of the same automata set.
%Additionally, we have filtered one automaton from the \texttt{ltl3tela} set
%that cannot be processed by \telatko due to an extensive use of system
%resources.

@@

\begin{table}[b]
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
\begin{tabular}{lr@{~~~}lr}
\toprule
tool        & version&homepage & automata \\
\midrule
\texttt{ltl2dela} & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
\texttt{ltl2dgra} & 21.0 & & 234\\
\texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
\texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 paper/table-data.tex
new numbers

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\129 automata\\523 acc.~marks}}
&
level 1 &
387 & 26.0 & 796.9 & 111 & 18
\\
&
level 2 &
395 & 24.5 & 1057.1 & 108 & 21
\\
&
level 3 &
393 & 24.9 & 9366.6 & 104 & 25
\\
&
multi &
379 & 27.5 & 11486.6 & 104 & 25
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\234 automata\\882 acc.~marks}}
&
level 1 &
552 & 37.4 & 786.3 & 220 & 14
\\
&
level 2 &
569 & 35.5 & 956.2 & 216 & 18
\\
&
level 3 &
562 & 36.3 & 1276.4 & 211 & 23
\\
&
multi &
543 & 38.4 & 2525.3 & 211 & 23
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\70 automata\\198 acc.~marks}}
&
level 1 &
198 & 0.0 & 590.9 & 70 & 0
\\
&
level 2 &
198 & 0.0 & 630.8 & 70 & 0
\\
&
level 3 &
189 & 4.5 & 2127.0 & 63 & 7
\\
&
multi &
189 & 4.5 & 2180.6 & 64 & 6
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\90 automata\\343 acc.~marks}}
&
level 1 &
328 & 4.4 & 486.5 & 78 & 12
\\
&
level 2 &
330 & 3.8 & 567.0 & 75 & 15
\\
&
level 3 &
322 & 6.1 & 717.0 & 71 & 19
\\
&
multi &
319 & 7.0 & 1622.5 & 72 & 18
\\

>>>>

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\129 automata\\523 acc.~marks}}
&
level 1 &
387 & 26.0 & 736.5 & 111 & 18
\\
&
level 2 &
395 & 24.5 & 954.6 & 108 & 21
\\
&
level 3 &
397 & 24.1 & 7089.0 & 103 & 26
\\
&
multi &
379 & 27.5 & 9128.6 & 105 & 24
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\234 automata\\882 acc.~marks}}
&
level 1 &
552 & 37.4 & 718.7 & 220 & 14
\\
&
level 2 &
569 & 35.5 & 866.0 & 216 & 18
\\
&
level 3 &
561 & 36.4 & 1148.5 & 213 & 21
\\
&
multi &
543 & 38.4 & 2310.9 & 211 & 23
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\70 automata\\198 acc.~marks}}
&
level 1 &
198 & 0.0 & 34.6 & 70 & 0
\\
&
level 2 &
198 & 0.0 & 66.4 & 70 & 0
\\
&
level 3 &
189 & 4.5 & 1256.5 & 63 & 7
\\
&
multi &
189 & 4.5 & 1288.2 & 64 & 6
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\91 automata\\348 acc.~marks}}
&
level 1 &
332 & 4.6 & 454.3 & 79 & 12
\\
&
level 2 &
334 & 4.0 & 537.8 & 76 & 15
\\
&
level 3 &
326 & 6.3 & 680.7 & 72 & 19
\\
&
multi &
323 & 7.2 & 1548.2 & 73 & 18
\\
